### 2010-06-20 trunk/paper/IIWAS2010/content/introduction.tex
IIWAS 2010 submission: Initial draft

\section{Introduction}
% Christan
When traveling though a jungle to a destination, it is easy to get lost.  The first person to go somewhere may make a number of mistakes in trying to find the best path to their destination.  However, those who come later will find it easy to reach that destination if a well-marked trail has been created. Olsen and Malizia describe this idea as \emph{exploiting trails} \cite{5379671}.  Rather than treating a user's search as a unique entity and working without an example context, one can exploit the fact that a similar search may have been performed already.  In one study, almost 40 percent of all queries were found to be repetitions of previous queries\cite{1277770}. This indicates the reuse of prior searches is a way to optimize the search process.  We have built a prototype system for answering questions using deep-web sources that employs previously answered questions to obtain new answers.  Using our analogy, the Morpheus question answering system follows path-finders to their destinations and not only marks the trail, but also provides a taxi service to take followers to similar destinations.

>>>>

\section{Introduction}

% Outline 
% ---------------------

% 1. Motivation 
% 2. What are we proposing?  
% 3. Challenges
% 		3.1 User query processing 
% 		3.1 Need of an ontology 
% 4. Realm based question answering 
% 5. About the paper structure

When traveling though a jungle to a destination, it is easy to get
lost.  The first person to go somewhere may make a number of mistakes
in trying to find the best path to their destination.  However, those
who come later will find it easy to reach that destination if a
well-marked trail has been created. Olsen and Malizia describe this
idea as \emph{exploiting trails} \cite{5379671}.  Rather than treating
a user's search as a unique entity and working without an example
context, one can exploit the fact that a similar search may have been
performed already.  In one study, almost 40 percent of all queries
were found to be repetitions of previous queries\cite{1277770}. This
indicates the reuse of prior searches is a way to optimize the search
process.  Morpheus is a question answering system motivated by reuse of prior web search pathways to yield an answer a user query. Using our analogy, Morpheus  follows path-finders to their destinations and not only marks the trail, but also provides a taxi service to take followers to similar destinations.

The Morpheus system employs two types of users. One type is called a
\textit{guide user} who types queries in the Morpheus web interface and
searches for an answer to the query in an instrumented web browser that can
track answer pathways for a given query. This web tracking tool stores the query
and necessary information to revisit the pathways to the page where he or she
finds the answer. It also provides users a mechanism to highlight the answers.
The other type is a \textit{regular user}, who uses the Morpheus system much
like a regular search engine with a natural language interface. He can type a
question in a text box and receive a response from the system. The system
exploits previously answered queries to answer new questions.

To exploit the prior searches one should represent queries in an elegant way so
that similar queries can be found efficiently and their stored search path
revisited to produce answer to the user. Morpheus represents user-query details in a semi structured format called a Semi-Structured Query or \textit{SSQ}. It includes a user query in natural language format, relevant terms for the query, place holders for the term \textit{categories}. A category represents a \textit{topic} or \textit{class} that a term belongs. For example, the term \textit{tire} can be classified into the category \textit{Automotive Parts}.

In addition, Morpheus assumes term categories are come from a \textit{consistent} realm-based ontology. By consistency, we mean it has a clean taxonomy of classes in the ontology class heterachy. This is important because, our proposed similarity measure for categories is based on the heterarchical structure of category ontology. Moreover, when a regular user enters a query, Morpheus ranks SSQs in the store based on this catgeory similarity. Suppose a regular user asks -\textit{ a 1997 Toyota Camry V6 needs what size tires?}. In this query, identifying \textit{Camry V6} as a subclass of \textit{Toyota} cars and a predecessor of \textit{automobile models} is important, because this will help us grouping stored queries. Similarly, a clean ontology-taxonomy can improve the recall of such queries by supporting transitivity and other types of inference like faceted browing \cite{Wu2008}.

This paper starts with disussing state-of-the-art systems in the area of question answering, ontology generation, and query ranking. The section system architecture explains the Morpheus system and its implementations details. In the results section, we describe current results and its interpretations. Finally, we conclude the paper by describing the global impacts of our approaches in QA systems, WWW page categorization, and ontology generators.

### 2010-06-20 trunk/paper/IIWAS2010/content/related_work.tex

\section{Related Work}

1. QA systems 
2. Ontology generators 
3. NLP interfaces

>>>>

\section{Related Work}
\label{sec:relatedwork}

\subsection{Question Ansering Systems}

\subsection{Ontology generators}

An ontology formally models real world \textit{concepts} and their
relationships. A concept or class in an ontology gives us an abstract and simplified view of the world\cite{Gruber1993} in a machine-readable and
language-independent format. The relationships and attributes of an
ontological concept are defined using \textit{properties} and \textit{property
restrictions}. An ontology definition contains all of
these: classes, properties, and restrictions. A class in an ontology can have
multiple \textit{super classes} and \textit{sub-classes}. Finally, a \textit{knowledge base} represents an ontology together with 
instances of its classes.

The DBpedia\footnote{http://dbpedia.org} project is based on extracting
semantic information from the Wikipedia and making it available on the
Web. Wikipedia semantics includes info-box templates, categorization
information, images, Geo-coordinates, links to external Web pages,
disambiguation pages, and redirects between pages in Wiki markup form
\cite{Auer07dbpedia:a, Bizer2009}.

The extraction procedure is as follows: Wikipedia categories are represented
using skos:concepts and category relations are represented using skos:broader
\cite{Auer07dbpedia:a, Bizer2009}. In fact, DBpedia does not define any new
relation between the Wikipedia categories. The Wikipedia categories are
extracted directly from Wikipedia pages and there is no quality check on the
resultant ontology. Similarly, DBpedia uses the info-box attributes and values
as the ontological relations and its ranges.

YAGO is a partly automatically constructed ontology from Wikipedia and
WordNet\cite{Suchanek2009phd}. The YAGO ontology uses an automated process to
extract information from Wikipedia pages, info-boxes, and categories and to
combine this information with the WordNet\footnote{http://wordnet.princeton.edu} synsets heterarchy. Since Wikipedia contains more individuals in the form of Wikipedia pages than in the man-made WordNet ontology, the Wikipedia page titles are used as the YAGO ontology individuals. YAGO concentrates mainly on the fields of people, cities, events, and movies\cite{Suchanek2009phd}.

In addition, YAGO uses Wikipedia categories as its ontology classes. The ontology's heterarchy is built using the \textit{hypernym} and \textit{hyponym} relations of the WordNet synsets. YAGO uses only the nouns from WordNet and ignores the WordNet verbs and adjectives. The connection between a WordNet synset and a Wikipedia category is achieved by parsing the category names and matching the parsed category components with the WordNet synsets\cite{Suchanek2009phd}. Those Wikipedia categories having no WordNet match are ignored in the YAGO ontology.

Moreover, YAGO type extraction is mainly based on the assumption that
each Wikipedia page has at least one tagged category, and the assigned Wikipedia
categories are relevant to that Wikipedia page. The Wikipedia page category assignments are subjectively assigned by human editors and some Wiki pages could be left unassigned i.e., they have no category unintentionally. In addition, we cannot completely rely on the relevance of these assigned Wikipedia page categories. To overcome these issues, we propose an automatic Wikipedia page categorization or classification and recommendation using a machine learning technique, topic modeling.

\subsection{NLP Interfaces}
